Contention Management for 5G

### 2017-05-18 article/article.tex

@@

     \subsubsection{Another better Algorithm than LSG: optimal on PT}

@@

     This algorithm uses the exact same greedy scheduling than LSG. Nevertheless, when it tries to schedule a message that is not able to totally pass $c_t$ before it's deadline (let us call \em{crisis message} this message), the algorithm call a subroutine that reschedule the previous message such that the crisis message will be scheduled earlier.

     \subsubsection{Mix : Simons periodic}

>>>>

    By using a binary heap to manage the eligible routes, this algorithm runs in $\mathcal{O}(n\log{}n)$.

@@

     \subsubsection{Another better Algorithm than Greedy: optimal on PT}

@@

     This algorithm uses the exact same greedy scheduling than LSG. Nevertheless, when it tries to schedule a message that is not able to totally pass $c_t$ before it's deadline (let us call \em{crisis message} this message), the algorithm call a subroutine which, following some criteria, removes some previous messages such that the crisis message can be scheduled earlier.

     If this algorithm gives us a $(P,\tau)$ periodic affectation, it satisfies the criteria $MT({\cal M}) < T_{max}$ Also, the algorithm minimizes $MT({\cal M})$, but does not ensure the periodicity.

     \subsubsection{Final algorithm}

     We adapted the optimal algorithm presented in the previous paragraph, to ensure a periodic $(P,\tau)$ periodic affectation, if it exists, with the given offsets, which are determined by the sending order chose.

    \begin{algorithm}[H]
    \caption{Optimal Periodic}
    \begin{algorithmic}
    \REQUIRE A routage graph ${\cal R_{\cal C}}$,a period $P$, packet size $\tau$, the offsets $m_i$
    \ENSURE $(P-\tau)-$periodic affectation of ${\cal R_{\cal C}}$, if it exists

    \FORALL{route $r_{t_i}$}
    \STATE  $w_i \leftarrow 0$
    \STATE $end-period \leftarrow m_{s_i} + \lambda(r_{s_i}) + t(c_t,r_{t_i}) + P$
    \FORALL{route $r_{t_j}$}
    \STATE $deadline-route \leftarrow m_{s_j} + T_{max}-t(c_s,r_{s_j})$
    \STATE $deadline \leftarrow (deadline-route,end-period)$
    \ENDFOR

    \STATE Call the optimal algorithm

    \ENDFOR

    \STATE return the best $(P-\tau)-$periodic affectation, or FAILURE

    This algorithm runs in $\mathcal{O}(n^3\log{}n)$. It tries for every routes of the routage graph, to fix the first route to comeback, and then determine the deadline of the other routes taking the minimum between the end of the period (determined by the first message that we fixed), and the deadline of the route itself(determined by $m_{s_i} + T_{max}-t(c_s,r_{s_i})$).

    This algorithm guarantee an optimal scheduling for the messages, if it exists, once the offsets $m_i$ has been fixed. The goal is to choose the best starting order, such that we have a good chance to have a $(P,\tau)$ periodic affectation, even with a small period, and T$_{max}$.

    \subsubsection{Results}

    \paragraph{Comparer les departs}

    \paragraph{Comparer les retours}

    \paragraph{Comparer optimal + depart random avec stochastique}
